\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-11-05 chapters/5_experiments_noise.tex
Fix some mistakes and polish CS results
Restructure for CVPR submission

@@

\begin{figure}[t]
        \centering
\begin{minipage}[t]{0.56\textwidth}
    \centering
    \scriptsize
        \begin{tabular}[t]{l|c}
          & \makecell{CREMI-Score \\(lower is better)} \\ \midrule 
\textbf{\algname{}} \textbf{Average}& \textbf{0.226}  \\
\algname{} Sum + Constraints \cite{levinkov2017comparative} & 0.282 \\
\algname{} Abs. Max. \cite{wolf2018mutex} & 0.322 \\
\algname{} Max. + Constraints & 0.324 \\
\algname{} Sum \cite{keuper2015efficient} & 0.334 \\
\algname{} Average + Constraints & 0.563 \\
THRESH & 1.521 \\ 
        \end{tabular}
    \captionof{table}{CREMI-Scores achieved by different linkage criteria and thresholding. All methods use the affinity predictions from our CNN as input. Scores are averages over the three CREMI training datasets.}
    \label{tab:results_cremi_train}
\end{minipage}\hfill
\begin{minipage}[t]{0.4\textwidth}
    \centering
    \scriptsize
        \begin{tabular}[t]{l|c}
         & \makecell{CREMI-Score \\(lower is better)}  \\ \midrule
Our CNN + DTWS + LMC &  0.221\\
PNI CNN \cite{lee2017superhuman} & 0.228 \\
\textbf{Our CNN + \algname{} Average} & \textbf{0.241} \\
MALA CNN + MC \cite{funke2018large} & 0.276 \\
CRU-Net \cite{zeng2017deepem3d} & 0.566  \\
LFC \cite{parag2017anisotropic} & 0.616  \\
        \end{tabular}
        \vspace*{1em}
    \captionof{table}{Current leading entries  in the CREMI challenge leaderboard \cite{cremiChallenge} (May 2019). The scores are averages of the three test datasets.}
    \label{tab:results_cremi_test}
\end{minipage}
\end{figure}
\captionsetup[subfigure]{justification=centering, singlelinecheck=off}
\begin{figure}
\centering
    \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.55in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_0.pdf}
    \end{subfigure} \hfill
    \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_1.pdf}
    \end{subfigure}

        \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_0.pdf}
        \caption{No long-range predictions: $p_{\mathrm{long}}=0$} \label{fig:merge_noise_only_direct}
    \end{subfigure} \hfill
    \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_1.pdf}
        \caption{With long-range predictions: $p_{\mathrm{long}}=0.1$} \label{fig:merge_noise_with_long_range}
    \end{subfigure}
\caption{\algname{} sensitivity to noise: \emph{Average} linkage proved to be the most robust. Performances are given by Rand-Score (higher is better) depending on the amount of noise added to the CNN predictions. Solid lines represent median values over 30 experiments. Values between the 25th and the 75th percentile are shown in shaded areas. The two sets of experiments using under- and over-clustering noise are summarized in the plots at the top and at the bottom, respectively (see Appendix \ref{sec:appendix_noise_gen} for more details). For each experiment, some of the long-range CNN predictions were randomly selected with probability $p_{\mathrm{long}}$ and added as long-range edges to the pixel grid-graph.
}\label{fig:noise_plots}
\end{figure}

>>>>

\captionsetup[subfigure]{justification=centering, singlelinecheck=off}
\begin{figure*}
\centering
    \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.55in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_0.pdf}
    \end{subfigure} \hfill
    \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_1.pdf}
    \end{subfigure}

        \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_0.pdf}
        \caption{No long-range predictions: $p_{\mathrm{long}}=0$} \label{fig:merge_noise_only_direct}
    \end{subfigure} \hfill
    \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_1.pdf}
        \caption{With long-range predictions: $p_{\mathrm{long}}=0.1$} \label{fig:merge_noise_with_long_range}
    \end{subfigure}
\caption{\algname{} sensitivity to noise: \emph{Average} linkage proved to be the most robust. Performances are given by Rand-Score (higher is better) depending on the amount of noise added to the CNN predictions. Solid lines represent median values over 30 experiments. Values between the 25th and the 75th percentile are shown in shaded areas. The two sets of experiments using under- and over-clustering noise are summarized in the plots at the top and at the bottom, respectively (see Appendix \ref{sec:appendix_noise_gen} for more details). For each experiment, some of the long-range CNN predictions were randomly selected with probability $p_{\mathrm{long}}$ and added as long-range edges to the pixel grid-graph. Experiments are performed on a crop of CREMI training sample B.
}\label{fig:noise_plots}
\end{figure*}
\begin{figure*}[t]
        \centering
\begin{minipage}[t]{0.31\textwidth}
    \centering
    \scriptsize
        \begin{tabular}[t]{l|c}
          & \makecell{CREMI-Score \\(lower is better)} \\ \midrule 
\textbf{\algname{}} \textbf{Average}& \textbf{0.226}  \\
\algname{} Sum + Constraints \cite{levinkov2017comparative} & 0.282 \\
\algname{} Abs. Max. \cite{wolf2018mutex} & 0.322 \\
\algname{} Max. + Constraints & 0.324 \\
\algname{} Sum \cite{keuper2015efficient} & 0.334 \\
\algname{} Average + Constraints & 0.563 \\
THRESH & 1.521 \\ 
        \end{tabular}
    \captionof{table}{CREMI-Scores achieved by different linkage criteria and thresholding. All methods use the affinity predictions from our CNN as input. Scores are averages over the three CREMI training datasets.}
    \label{tab:results_cremi_train}
\end{minipage}\hfill
\begin{minipage}[t]{0.3\textwidth}
    \centering
    \scriptsize
        \begin{tabular}[t]{l|c}
         & \makecell{CREMI-Score \\(lower is better)}  \\ \midrule
Our CNN + DTWS + LMC &  0.221\\
PNI CNN \cite{lee2017superhuman} & 0.228 \\
\textbf{Our CNN + \algname{} Average} & \textbf{0.241} \\
MALA CNN + MC \cite{funke2018large} & 0.276 \\
CRU-Net \cite{zeng2017deepem3d} & 0.566  \\
LFC \cite{parag2017anisotropic} & 0.616  \\
        \end{tabular}
        \vspace*{4.5em}
    \captionof{table}{Current leading entries  in the CREMI challenge leaderboard \cite{cremiChallenge} (May 2019). The scores are averages of the three test datasets.}
    \label{tab:results_cremi_test}
\end{minipage}\hfill
\begin{minipage}[t]{0.32\textwidth}
\centering
    \scriptsize
    \vspace*{-1.5em}
\begin{tabular}[t]{l|cc}
            & AP  & AP 50\% \\ 
        Method & \multicolumn{2}{c}{(higher is better)} \\ \midrule
           Panoptic-DeepLab \cite{cheng2019panopticdeeplab} & 34.6 & 57.3 \\
           UPSNet \cite{xiong2019upsnet} $\dagger$ & 33.0 & 59.6 \\
           SSAP \cite{Gao_2019_ICCV} & 32.7 & 51.8 \\
           PANet \cite{liu2018path} $\dagger$ & 31.8 & 57.1 \\
           \textbf{GMIS Model + \algname{} Average} & \textbf{28.3} & \textbf{47.0} \\ 
           JOSECB \cite{neven2019instance} & 27.7 & 50.9 \\
           \textbf{GMIS Model} \cite{liu2018affinity} & \textbf{27.3} & \textbf{45.6} \\
           Mask R-CNN \cite{he2017mask} $\dagger$ & 26.2 & 49.9 \\
           SGN \cite{liu2017sgn} & 25.0 & 44.9 \\
           % DIN \cite{arnab2017pixelwise} & 20.0 & 38.8 \\
           DWT \cite{bai2017deep} & 19.4 & 35.3 \\
           InstanceCut \cite{kirillov2017instancecut} & 13.0 & 27.9 \\
        \end{tabular}
    % \caption{CityScapes \emph{test} set}
    \vspace*{0.7em}
    \captionof{table}{Average Precision scores on CityScapes test. Methods marked with $\dagger$ are \emph{proposal-based}.}\label{tab:results_cityscapes}
    \label{tab:results_cityscapes_test}
\end{minipage}
\end{figure*}

\captionsetup[subtable]{labelformat=simple, labelsep=space, justification=centering, singlelinecheck=off}
\renewcommand*{\thesubtable}{(\alph{subtable})}
\begin{figure*}[t]
\begin{minipage}{0.65 \textwidth}
\centering
\includegraphics[width=\textwidth]{./figs/cityscapes_compare_5.eps} % left bottom right top
\caption{Visual results given by different \algname{} linkage criteria on a crop of a CityScapes image}\label{fig:cityscapes}
\end{minipage}\hfill
\begin{minipage}{0.3 \textwidth}
    \centering
    \small
        \begin{tabular}[t]{l|cc}
             Agglomeration type & AP \\ \midrule
            % PANet \cite{liu2018path} & - & \textbf{36.5} \\
            % Mask R-CNN \cite{he2017mask} & - & 31.5 \\ \hline
              \algname{} Average& 34.3 \\
              \algname{} Average + Constraints & 33.9 \\
             MultiStepHAC \cite{liu2018affinity} & 33.0 \\
              \algname{} Abs. Max. \cite{wolf2018mutex}  & 32.1 \\
              \algname{} Sum + Constraints  \cite{levinkov2017comparative} & 31.9  \\
              \algname{} Sum \cite{keuper2015efficient} & 31.3 \\
        \end{tabular}
    \vspace*{0.6em}
    \caption{Average Precision scores on CityScapes \emph{val} achieved by the GMIS Model \cite{liu2018affinity} and different graph agglomeration methods.}
    \label{tab:results_cityscapes_val}
\end{minipage}
\end{figure*}

@@
